A mechanization of semi-simplicial and semi-cubical sets in the calculus of inductive constructions

### 2022-09-27 paper/paper.tex
paper: MAJ

  \begin{align*}
    \obj(\DeltaPlus) & := \Nat                                                                    \\
    \hom(p, n)       & := \{\{i_{p + 1}, \ldots, i_n\} \mid 0 < i_{p + 1} < \ldots < i_n \leq n\} \\
    g \circ f        & :=
    \begin{cases}
      g                          & \text{if f = \{\}}                                    \\
      f                          & \text{if g = \{\}}                                    \\
      b :: (g \circ f')          & \text{if g = (a :: g'), f = (b :: f'), with b < a}    \\
      a :: (g' \circ \uparrow f) & \text{if g = (a :: g'), f = (b :: f'), with b \geq a} \\
    \end{cases}            \\
    \id              & := \{\}
  \end{align*}

  Composition can be shown to be associative.
\end{definition}

@@

\begin{example}[$\DeltaPlus^1$]
  In dimension $1$, the standard augmented semi-simplex is simply the unit type:

  \begin{equation*}
    \begin{tikzcd}
      \star
    \end{tikzcd}
  \end{equation*}
\end{example}

\begin{example}[$\DeltaPlus^2$]
  In dimension $2$, it is
  \begin{equation*}
    \begin{tikzcd}
      \kstar0 \arrow[r, dash, "\kstar\kstar"] & 0\kstar
    \end{tikzcd}
  \end{equation*}
\end{example}

@@

\subsection{Semi-cubical sets}
\begin{notation}[Faces of cube]
  We use $\epsilon$ to indicate opposite faces of a cube; it takes values $+$ or $-$.
\end{notation}

\begin{definition}[\Cube]
  \begin{align*}
    \obj(\Cube)        & := \Nat                                                                                                             \\
    \hom(p, n)         & := \{(i_{p + 1}, \epsilon_{p + 1}) \ldots, (i_n, \epsilon_n) \mid p < i_{p + 1} < i_{p + 2} < \ldots < i_n \leq n\} \\
    g \circ f          & :=                                                                                                                  \\
    \id \in \hom(n, n) & := \{\}                                                                                                             \\
  \end{align*}
\end{definition}

@@

\begin{example}[$\Cube^0$]
  $\Cube^0$ is the empty set:

@@

\begin{example}[$\Cube^1$]
  \begin{equation*}
    \begin{tikzcd}
      0 \arrow[r, "\kstar", dash] & 1
    \end{tikzcd}
  \end{equation*}
\end{example}

>>>>

  \begin{align*}
    \obj(\DeltaPlus) & := \Nat                                                                    \\
    \hom(p, n)       & := \{\{i_{p + 1}, \ldots, i_n\} \mid 0 < i_{p + 1} < \ldots < i_n \leq n\} \\
    g \circ f        & :=
    \begin{cases}
      g                          & \text{if f = \{\}}                                          \\
      f                          & \text{if g = \{\}}                                          \\
      b :: (g \circ f')          & \text{if $g = (a :: g')$, $f = (b :: f')$, with $b < a$}    \\
      a :: (g' \circ \uparrow f) & \text{if $g = (a :: g')$, $f = (b :: f')$, with $b \geq a$} \\
    \end{cases}      \\
    \id              & := \{\}
  \end{align*}

  Evidently, $\id$ is neutral. Further, composition can be shown to be associative.
\end{definition}

\begin{definition}[Alternative definition of $\DeltaPlus$]
  \begin{align*}
    \obj(\DeltaPlus) & := \Nat                                                                     \\
    \hom(p, n)       & := \{l \in \{0, \kstar\}^n \mid \text{number of $\kstar$ in l = p}\}        \\
    g \circ f        & :=
    \begin{cases}
      f                  & \text{if $g = \{\}$}                                                      \\
      0 :: (g' \circ f)  & \text{if $g = (0 :: g')$}                                                 \\
      a :: (g' \circ f') & \text{if $g = (\star :: g')$, $f = (a :: f')$, where $a = 0$ or $\kstar$} \\
    \end{cases} \\
    \id              & := \{\kstar, \ldots, \kstar\} \text{ $n$ times}
  \end{align*}

  Note that, if $g \circ f$ is well-defined, then the length of $f$ is less than that of $g$. It can be shown that composition is associative and that $\id$ is neutral.
\end{definition}

@@

\begin{example}[$\DeltaPlus^1$]
  In dimension $1$, the standard augmented semi-simplex can be pictured as a point, where the color is kept implicit. This point is the identity in $\Hom(1, 1)$; it is hence shown as a singleton $\kstar$:

  \begin{equation*}
    \begin{tikzcd}
      \kstar
    \end{tikzcd}
  \end{equation*}
\end{example}

\begin{example}[$\DeltaPlus^2$]
  In dimension $2$,
  \begin{equation*}
    \begin{tikzcd}
      \kstar0 \arrow[r, dash, "\kstar\kstar"] & 0\kstar
    \end{tikzcd}
  \end{equation*}
\end{example}

@@

\subsection{Semi-cubical sets}
\begin{definition}[\Cube]
  $\Cube$ is defined similarly to $\DeltaPlus$, except that we take $0$, $1$ and $\star$, instead of $0$ and $\kstar$. We use $0$ and $1$ to indicate opposite faces of a cube.

  \begin{align*}
    \obj(\DeltaPlus) & := \Nat                                                                     \\
    \hom(p, n)       & := \{l \in \{0, 1, \kstar\}^n \mid \text{number of $\kstar$ in l = p}\}     \\
    g \circ f        & :=
    \begin{cases}
      f                  & \text{if $g = \{\}$}                                                      \\
      0 :: (g' \circ f)  & \text{if $g = (0 :: g')$}                                                 \\
      a :: (g' \circ f') & \text{if $g = (\star :: g')$, $f = (a :: f')$, where $a = 0$ or $\kstar$} \\
    \end{cases} \\
    \id              & := \{\kstar, \ldots, \kstar\} \text{ $n$ times}
  \end{align*}
\end{definition}

@@

\begin{example}[$\Cube^0$]
  $\Cube^0$ is $\Hom(0, 0)$, or the empty set:

@@

\begin{example}[$\Cube^1$]
  $\Cube^1$ is two points and a line:
  \begin{equation*}
    \begin{tikzcd}
      0 \arrow[r, "\kstar", dash] & 1
    \end{tikzcd}
  \end{equation*}
\end{example}
